Fast and Flexible Dynamic Binary Translation for the Kernel

### 2013-12-18 VEE-14/paper.tex
Minor updates to the optimizations section.

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{Fast and Flexible Binary Instrumentation for the Kernel}

@@

Granary's tracing strategy is based on the observation that the most commonly executed path through code follows a straight line. That is, execution is more likely to fall through a conditional CTI than it is to take the conditional CTI. We experimentally verified Granary's tracing strategy by disabling tracing and relying on Granary's internal performance counters to count how many conditional branches were patched (by their edge code, \texttildelow 25\%), versus how many synthesized fall-through \texttt{jmp}s were patched (\texttildelow 80\%).

@@

One approach to change an instruction's alignment is to pad the basic block with additional \texttt{nop} instructions. An alternative when more than a few bytes of padding are needed is to introduce a single control-flow instruction (\texttt{jmp}) that jumps around the padded area. However, adding extra instructions introduces latency into the processor's fetch/decode/execute cycle. Therefore, when possible, Granary uses ignored instruction prefixes to alter an instruction's alignment. For example, Granary aligns patchable conditional jumps using static branch prediction hint prefixes, which are ignored by recent x86-64 processors \cite{AgnerMicroarchitecture}. Finally, most basic blocks are small (i.e. fit in one cache line), therefore, aligning basic blocks on cache line boundaries naturally avoids the potential for a patchable instruction to straddle two cache lines.

@@

\toolname{RCUdbg} detects the the following RCU bugs related to misuses of RCU-protected pointers.
\begin{itemize}[leftmargin=3.2em]
	\item[B1)] Reads through an RCU-dereferenced pointer outside of a read-side critical section (\Cref{fig:rcu_existence_bug}).
	\item[B2)] Reads through an RCU-dereferenced pointer in the wrong read-side critical section.

	\item[B2)] Reads through an RCU-assigned pointer that don't first use \texttt{rcu\_dereference} (\Cref{fig:rcu_deref_bug}).
	\item[B3)] Reads through fields of RCU-protected data structures that should be accessed via \texttt{rcu\_dereference} (\Cref{fig:rcu_assign_bug}).

	\item[B5)] Writes through an RCU-dereferenced pointer.
	\item[B6)] Writes through an RCU-assigned pointer by a non-write thread.
\end{itemize}

>>>>

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{Fast and Flexible Dynamic Binary Translation for the Kernel}

@@

Granary's tracing strategy is based on the observation that the most commonly executed path through code follows a straight line. That is, execution is more likely to fall through a conditional CTI than it is to take the conditional CTI. We experimentally verified Granary's tracing strategy by disabling tracing and relying on Granary's internal performance counters to count how many conditional branches were patched (by their edge code, \texttildelow 35\%), versus how many synthesized fall-through \texttt{jmp}s were patched (\texttildelow 80\%).

Profile-guided ahead-of-time tracing further improves on Granary's otherwise na\"{i}ve tracing strategy by integrating profile information from Granary's \toolname{cfg} tool (\Cref{sec:cfg}).

@@

One approach to change an instruction's alignment is to pad the basic block with additional \texttt{nop} instructions. An alternative when more than a few bytes of padding are needed is to introduce a single control-flow instruction (\texttt{jmp}) that jumps around the padded area. However, adding extra instructions introduces latency into the processor's fetch/decode/execute cycle. Therefore, when possible, Granary uses ignored instruction prefixes to alter an instruction's alignment. For example, Granary aligns patchable conditional jumps using static branch prediction hint prefixes, which are ignored by recent x86-64 processors \cite{AgnerMicroarchitecture}. When possible, alignment requirements are reduced by allowing a patchable instruction to straddle a cache line, but for the part to be patched to be fully contained by a single cache line. Finally, most basic blocks are small (i.e. fit in one cache line), therefore, aligning basic blocks on cache line boundaries naturally avoids the potential for a patchable instruction to straddle two cache lines.

@@

\toolname{RCUdbg} detects the the following RCU bugs related to misuses of RCU-protected pointers.
\begin{itemize}[leftmargin=3.2em]
	\item[\bf B1] Reads through an RCU-dereferenced pointer outside of a read-side critical section (\Cref{fig:rcu_existence_bug}).
	\item[\bf B2] Reads through an RCU-dereferenced pointer in the wrong read-side critical section.

	\item[\bf B2] Reads through an RCU-assigned pointer that don't first use \texttt{rcu\_dereference} (\Cref{fig:rcu_deref_bug}).
	\item[\bf B3] Reads through fields of RCU-protected data structures that should be accessed via \texttt{rcu\_dereference} (\Cref{fig:rcu_assign_bug}).

	\item[\bf B5] Writes through an RCU-dereferenced pointer.
	\item[\bf B6] Writes through an RCU-assigned pointer by a non-write thread.
\end{itemize}
